From Real-time Attention Assessment to ``With-me-ness'' in Human-Robot Interaction

### 2015-10-01 paper.tex
Recomputed Cohen's kappa for inter-rater reliability

We video-recorded the interactions, and performed a {\it post-hoc} manual coding
of the focus of attention with two annotators (Cronbach's
$\alpha=.89$)\fixme{did the 2nd annotator annotated the 6 whole interactions?}.
The manual coding forms our attentional \emph{ground-truth}.

>>>>

We video-recorded the interactions, and performed a {\it post-hoc} manual coding
of the focus of attention (24\% double-coded, Cohen's $\kappa=0.91$, high
reliability).  The manual coding forms our attentional \emph{ground-truth}.
